---
title: "ESM 206 Lab 7: Multiple linear regression"
author: "Claire Gonzales"
date: "11/8/2021"
output: html_document
---

```{r setup, include=TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Attach packages
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
```


## Intro to ggpairs

Use GGally::ggpairs() funciton to create a pairs plot.
```{r}
# this takes a while to run becuase it gives you so many things
ggpairs(penguins)
```

```{r}
# So now we are going to do this in a more focused way

penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))

# This gives a plot with only the things we 'selected' so it's easier to read

# Now i might want to lo0ok at something specifically

ggplot(data = penguins, aes(x = bill_depth_mm, y = body_mass_g)) +
  geom_point(aes(color = species))

# Alternately, we can tell r that there is an important variable to group by:
ggplot(data = penguins, aes(x = bill_depth_mm, y = body_mass_g, group = species)) +
  geom_point() +
  geom_smooth(method = "lm")

```


## Multiple linear regression - penguins

We are going to try to use multiple linear regressions to try to understand the relationship between multiple predictor variables and a single continuous outcome variable (body mass).

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

#return just the coefficients:
penguin_lm

```

How would you interpret the coefficient for flipper length?
"If everything else stays constant, on average we would except a 51.54g increase in body mass for each 1mm increase in flipper length"

Also, we can use `summary()` function
```{r}
summary(penguin_lm)
```

"R-squared values means that 76% of variants are explained by this model"
R squared value cannot be deemed as "good" or "bad".

### Use `broom` functions tidy and glance

Use broom::tidy to get the coefficiant summary in a data frame.
Use broom::glance to get the model summary in a data frame.

```{r}
penguin_lm_tidy <- tidy(penguin_lm)
penguin_lm_tidy

```

EX; Use in-line code to refer to the bill depth coefficient:

Bill depth coefficient is `r penguin_lm_tidy$estimate[3]`


```{r}
# Now using glance

penguin_lm_glance <- glance(penguin_lm)

penguin_lm_glance
# This might be a little easier to pull values from for in-line code purposes
```

